---
output:
  officedown::rdocx_document:
    pandoc_args: ["--metadata-file=header.yaml"]
params:
    cylcode: 6
---

# `r paste("Parameterized report for cars with", params$cylcode,"cylinders")`
Here are some results that repeat for each of several species. Here I will cross-reference to the first figure in this "chapter" (Figure \@ref(fig:firstinchap)), and here I will cross reference to the second figure in this chapter (Figure \@ref(fig:secondinchap)). You will notice that if you're reading the second parameterized chapter in the doc, these references will be Figure \@ref(fig:firstinchap) and Figure \@ref(fig:secondinchap). The index doesn't advance the same way the figure numbers in the captions do!

```{r echo=FALSE,fig.cap='First figure in parameterized document -- the figure number is 2 the first time it shows up, and 4 the second time it shows up.', fig.id='firstinchap',  tab.cap.style = "Figure Caption"}
p1 <- subset(x = mtcars,
                    cyl==params$cylcode)
plot(p1$mpg,p1$wt,pch=2)
```

Here's some more text, followed by a second figure. For each parameterized report thing, there will be two graphs. 

```{r echo=FALSE,fig.cap='Second figure in parameterized document -- the figure number is 3 the first time it shows up, and 5 the second time it shows up.', fig.id='secondinchap',  tab.cap.style = "Figure Caption"}
p2 <- subset(x = mtcars,
                    cyl==params$cylcode)
plot(p2$wt,p2$qsec,pch=19)
```